---
title: "Lifestyle Habits and Work Productivity Analysis"
output: html_notebook
---

```{r}
library(tidyverse)
library(ggplot2)
df <- read_csv("data.csv")
head(df)
```

```{r}
summary(df)
str(df)
```

```{r}
colSums(is.na(df))
```

```{r}
df <- df %>% rename(
  "ID" = "Person_ID",
  "Sleep Start" = "Sleep Start Time",
  "Sleep End" = "Sleep End Time",
  "Sleep Hours" = "Total Sleep Hours" ,
  "Exercise Time" = "Exercise (mins/day)",
  "Caffeine" = "Caffeine Intake (mg)",
  "Screen Time" = "Screen Time Before Bed (mins)",
  "Work Hours" = "Work Hours (hrs/day)",
  "Prod Score" = "Productivity Score",
  "Mood" = "Mood Score",
  "Stress" = "Stress Level"
)
```

```{r}
length(unique(df$ID))
```

```{r}
counts <- table(df$ID)
counts[counts > 3]
```

```{r}
df[df$ID %in% c(5597),]
```

```{r}
df <- df %>% select(-`ID`, -`Date`)
head(df)
```

```{r}
ggplot(df, aes(x = `Prod Score`)) +
  geom_histogram(binwidth = 1, fill = "cyan", color = "black", alpha = 0.5) +
  scale_x_continuous(breaks = 1:10) +
  labs(
    title = "Productivity Score", x = "Productivity Score", y = "Frequency")
```
```{r}
ggplot(df, aes(x = `Age`)) +
  geom_histogram(binwidth = 1, fill = "pink", color = "black", alpha = 0.5) +
  labs(title = "Age", x = "Age", y = "Frequency")
```
```{r}
ggplot(df, aes(x = `Sleep Hours`)) +
  geom_histogram(binwidth = 1, fill = "orange", color = "black", alpha = 0.5) +
  labs(title = "Sleep Hours", x = "Sleep Hours", y = "Frequency")
```
```{r}
ggplot(df, aes(x = `Gender`)) +
  geom_histogram(stat = "count", fill = "purple", color = "black", alpha = 0.5) +
  labs(title = "Gender", x = "Gender", y = "Frequency")
```
```{r}
ggplot(df, aes(x = `Sleep Quality`)) +
  geom_histogram(binwidth = 1, fill = "green", color = "black", alpha = 0.5) +
  scale_x_continuous(breaks = 1:10) +
  labs(title = "Sleep Quality", x = "Sleep Quality", y = "Frequency")
```
```{r}
ggplot(df, aes(x = `Mood`)) +
  geom_histogram(binwidth = 1, fill = "yellow", color = "black", alpha = 0.5) +
  scale_x_continuous(breaks = 1:10) +
  labs(title = "Mood", x = "Mood", y = "Frequency")
```
```{r}
ggplot(df, aes(x = `Stress`)) +
  geom_histogram(binwidth = 1, fill = "red", color = "black", alpha = 0.5) +
  scale_x_continuous(breaks = 1:10) +
  labs(title = "Stress Level", x = "Stress Level",y = "Frequency")
```
```{r}
ggplot(df, aes(x = `Exercise Time`)) +
  geom_histogram(binwidth = 10, fill = "blue", color = "black", alpha = 0.5) +
  labs(title = "Exercise Time", x = "Exercise Time",y = "Frequency")
```
```{r}
library(ggcorrplot)
corr_mat = round(cor(df[sapply(df, is.numeric)]),1)
ggcorrplot(corr_mat, lab = TRUE)
```
No correlation between features so predictive modelling is not possible. We can only generate inference about the population using given sample dataset.
We will be using Different Hypothesis testing method to test some hypothesis about the population.

One Sample T-Test:
1.) H0: Average sleep quality is 7.
    Ha: Average sleep quality is not equal to 7
2.) H0: Average productivity score is 7
    Ha: Average productivity score is not equal to 7

Two Sample T-Test:
1.) H0: There is no difference in average sleep quality of males and females.
    Ha: There is difference in average sleep quality of males and females.
2.) H0: There is no difference in average work hours between individuals with low stress and those with high stress.
    Ha: There is difference in average work hours between individuals with low stress and those with high stress.
    
ANOVA:
1.) H0: Productivity Score is same across different age group
    Ha: Productivity Score is different across different age group
2.) H0: Productivity Score is same across different stress levels
    Ha: Productivity Score is different across different stress levels
   
   
   
One Sample T-Test:
H0: Average sleep quality is 7.
Ha: Average sleep quality is not equal to 7
```{r}
t_test_sleep_quality <- t.test(df$`Sleep Quality`, mu = 7)
print("Sleep Quality T Test")
print(t_test_sleep_quality)
```
H0: Average productivity score is 7
Ha: Average productivity score is not equal to 7
```{r}
t_test_prod_score <- t.test(df$`Prod Score`, mu = 7)
print("Productivity Score T Test")
print(t_test_prod_score)
```
H0: There is no difference in average sleep quality of males and females.
Ha: There is difference in average sleep quality of males and females.
```{r}
male_df <- subset(df, `Gender` == "Male", select = `Sleep Quality`)
female_df <- subset(df, `Gender` == "Female", select = `Sleep Quality`)
t_test_gender_sleep <- t.test(male_df$`Sleep Quality`, female_df$`Sleep Quality`, var.equal = TRUE)
print("Gender's Sleep Quality T-Test")
print(t_test_gender_sleep)
```
H0: There is no difference in average work hours between individuals with low stress and those with high stress.
    Ha: There is difference in average work hours between individuals with low stress and those with high stress.
```{r}

```

